Probability

### 2018-09-20 DATA606/Probability.Rmd
Finalize DATA 606 Probability.Rmd

## 2.6 Dice rolls

@@

## 2.8 Poverty and language

@@

## 2.20 Assortative mating

@@

(c) What is the probability that a randomly chosen male respondent with brown eyes has a partner with blue eyes?  **19/54 = 0.3518519**

What about the probability of a randomly chosen male respondent with green eyes having a partner with blue eyes? **11/36 = 0.3055556**

@@

## 2.30 Books on a bookshelf

@@

## 2.38 Baggage fees

@@

```{r}
fees <- c(rep(0, 54), rep(25, 34), rep(35+25, 12))
mean(fees)
```

@@

```{r}
n <- 120
zero_fee <- n * .54
twenty_five_fee <- n * .34
sixty_fee <- n * .12
fees2 <-c(rep(0, zero_fee), rep(25, twenty_five_fee), rep(60, sixty_fee))
mean(fees2)
sd(fees2)
```

@@

## 2.44 Income and gender

>>>>

## 2.6 Dice Rolls

@@

## 2.8 Poverty and Language

@@

## 2.20 Assortative Mating

@@

(c) What is the probability that a randomly chosen male respondent with brown eyes has a partner with blue eyes?  **19/54 = 0.3518519**  What about the probability of a randomly chosen male respondent with green eyes having a partner with blue eyes? **11/36 = 0.3055556**

@@

## 2.30 Books on a Bookshelf

@@

## 2.38 Baggage Fees

@@

```{r}
get_fees <- function(n){
  zero_fee <- n * 0.54
  twenty_five_fee <- n * 0.34
  sixty_fee <- n * 0.12
  c(rep(0, zero_fee), rep(25, twenty_five_fee), rep(60, sixty_fee))
}
fees <- get_fees(100)
mean(fees)
```

@@

```{r}
fees_120 <-get_fees(120)
mean(fees_120)
sd(fees_120)
```

@@

## 2.44 Income and Gender
